---
name: Jonathan J.
surname: Maynard
position: "Research Scientist"
address: "Oregon State University"
phone: +1 530 848 4144
www: jonathanjmaynard.com
email: "jmaynard@nmsu.edu"
twitter: soilSpace
github: jjmaynard
linkedin: jonathanjmaynard
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```



# Skills

## Data Science

* Forecasting, machine learning, big data wrangling, process automation, Discrete Event Simulation, regression analysis, data quality enhancement, data visualization, classification, text mining

## Applications

* RStudio, SAS EG, SQL Server, Excel, Tableau

## Languages

* R, SAS (Base 9 Certified), SQL, VBA

## Leadership

* Former non-profit board member and president, presenting information to mid-size audience, mentorship of peers, explaining technical material to non-technical audience and management, oversight of interns, change management

# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.

# Education

```{r}
tibble::tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "MA, Economics", "Central Michigan University", "Mount Pleasant, MI", "2010 - 2012","Research Assistant for two professors",
   "MA, Economics", "Central Michigan University", "Mount Pleasant, MI", "2010 - 2012","Taught undergraduate Microeconomics",
   "MA, Economics", "Central Michigan University", "Mount Pleasant, MI", "2010 - 2012","Master's paper: Fare or Foul: The effects of public transit fare increases on auto fatalities",
  "BS, Business", "University of North Carolina", "Chapel Hill, NC", "2002 - 2006","Minor: Anthropology"
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Nobel Prizes

```{r}
tibble::tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications
```{r}
# pubs <- scholar::get_publications("nyU9_dIAAAAJ&hl") %>%
#   distinct(title, .keep_all = TRUE) %>%
#   transmute(bibtype = "Article", author = as.character(author),
#             title = as.character(title),
#             journaltitle = as.character(journal), year, key = row_number()) %>%
#   RefManageR::as.BibEntry() %>%
#   RefManageR::WriteBib("pubs.bib")
```

```{r}
bibliography_entries("JJMaynard.bib")
```